---
title: "Figures"
author: "Madelon Zwerink"
date: "2025-09-12"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(patchwork)
library(broom.mixed)
library(lme4)
library(flexplot)
library(slider)
library(mgcv)
library(gratia)
library(ggVennDiagram)
library(ggforce)
library(grid)
library(ggtext)
```

## Reading data

```{r, include=FALSE}
source('read_data_clean.R')
```

## Table 1: Missing data

```{r}
missing_frac <- dm %>%
  select(trial, participant, ptraceraw, ptrace, pupil, bl_incl, gaze_incl, segment) %>%
  mutate(
    frac_na_ptraceraw = round(map_dbl(ptraceraw, ~ {
      data <- unlist(.x)[0:750]
      total <- length(data)
      n_na <- sum(is.na(data))
      n_na / total
    }), digits = 2),
    missing_samples = trial_summary$missing_samples,
    frac_na_ptrace = map_dbl(ptrace, ~ {
      data <- unlist(.x)[0:750]
      total <- length(data)
      n_na <- sum(is.na(data))
      n_na / total
    })
  ) %>%
  select(!c(ptraceraw, ptrace, pupil))

summary_participant_samples <- missing_frac %>%
  group_by(participant, segment) %>%
  summarise(
    missing_raw = sum(frac_na_ptraceraw == 1),
    percentage_raw = round((sum(frac_na_ptraceraw == 1)/n()) * 100, digits = 1),
    missing_samples = sum(missing_samples),
    total_samples = 992 * n(),
    percentage_samples = round((missing_samples / total_samples) * 100, 1),
    incl_bl = sum(bl_incl == 1),  
    excl_bl = sum(bl_incl == 0),
    incl_gaze = sum(gaze_incl == 1),
    excl_gaze = sum(gaze_incl == 0),
    incl = sum(bl_incl == 1 & gaze_incl == 1),
    excl = sum(bl_incl == 0 | gaze_incl == 0),
    nr_trials = n()
  )

summary_all_samples <- summary_participant_samples %>%
  group_by(segment) %>%
  summarise(
    missing_raw = sum(missing_raw),
    percentage_raw = round((sum(missing_raw)/sum(nr_trials)) * 100, 1),
    missing_samples = sum(missing_samples),
    total_samples = sum(total_samples),
    percentage_samples = round((sum(missing_samples) / sum(total_samples)) * 100, 1),
    incl_bl = sum(incl_bl),
    excl_bl = sum(excl_bl),
    incl_gaze = sum(incl_gaze),
    excl_gaze = sum(excl_gaze),
    incl = sum(incl),
    excl = sum(excl),
    participant = "All participants"
  )

all_segments_samples <- summary_all_samples %>%
  summarise(
    missing_raw = sum(missing_raw),
    percentage_raw = round((sum(missing_raw)/sum(nr_trials)) * 100, 1),
    missing_samples = sum(missing_samples),
    total_samples = sum(total_samples),
    percentage_samples = round((sum(missing_samples) / sum(total_samples)) * 100, 1),
    incl_bl = sum(incl_bl),
    excl_bl = sum(excl_bl),
    incl_gaze = sum(incl_gaze),
    excl_gaze = sum(excl_gaze),
    incl = sum(incl),
    excl = sum(excl),
    participant = "All participants",
    segment = "All segments"
  )

per_participant_all_segments_samples <- summary_participant_samples %>%
  group_by(participant) %>%
  summarise(
    missing_raw = sum(missing_raw),
    percentage_raw = round((sum(missing_raw)/sum(nr_trials)) * 100, 1),
    missing_samples = sum(missing_samples),
    total_samples = sum(total_samples),
    percentage_samples = round((missing_samples / total_samples) * 100, 1),
    incl_bl = sum(incl_bl),
    excl_bl = sum(excl_bl),
    incl_gaze = sum(incl_gaze),
    excl_gaze = sum(excl_gaze),
    incl = sum(incl),
    excl = sum(excl),
    segment = "All segments"
  )

summary_combined <- bind_rows(
  all_segments_samples,
  per_participant_all_segments_samples,
  summary_all_samples,
  summary_participant_samples
)
```

```{r}
table1 <- summary_combined %>%
  mutate(formatted = paste0(missing_raw, " (", percentage_raw, "%)")) %>%
  select(segment, participant, formatted) %>%
  pivot_wider(
    names_from = participant,
    values_from = formatted
  )

table1
```

## Table 2: recorded samples

```{r}
table2 <- summary_combined %>%
  mutate(formatted = paste0(100 - percentage_samples, "%")) %>%
  select(segment, participant, formatted) %>%
  pivot_wider(
    names_from = participant,
    values_from = formatted
  )

table2
```

## Figure 2: Trackloss and gaze deviation

```{r}
trackloss <- dm_long %>%
  filter(time < 3900) %>%
  group_by(participant, time) %>%
  summarise(missing_datapoints = sum(ifelse(is.na(ptraceraw), 1, 0)),
            avg_xgaze = mean(dxtrace, na.rm = TRUE),
            avg_ygaze = mean(dytrace, na.rm = TRUE),
            sd_xgaze = sd(dxtrace, na.rm = TRUE),
            sd_ygaze = sd(dytrace, na.rm = TRUE))
```

```{r}
F2A <- ggplot(trackloss, aes(x = time, y = missing_datapoints)) +
      geom_bar(stat = 'identity', width = 4, alpha = 0.5, fill = 'darkgreen') +
      facet_wrap(vars(participant), nrow = 1) +
      theme_bw() +
      labs(x = 'Time relative to onset stimulus (ms)',
           y = 'Missing datapoints\n(count)') +
      ylim(0, 81) +
      theme(axis.title.x = element_blank())

F2B <- ggplot(trackloss, aes(x = time)) +
      annotate('segment', y = 0, x = 0, xend = 3900) +
      geom_line(aes(y = avg_xgaze), colour = 'darkgreen') +
      geom_ribbon(aes(ymin = avg_xgaze - sd_xgaze, ymax = avg_xgaze + sd_xgaze), alpha = 0.4, fill = 'darkgreen') +
      facet_wrap(vars(participant), nrow = 1) +
      theme_bw() +
      labs(x = 'Time relative to onset stimulus (ms)',
           y = 'Horizontal gaze deviation\n(pixels)') +
      theme(axis.title.x = element_blank(), strip.text = element_blank())

F2C <- ggplot(trackloss, aes(x = time)) +
      annotate('segment', y = 0, x = 0, xend = 3900) +
      geom_line(aes(y = avg_ygaze), colour = 'darkgreen') +
      geom_ribbon(aes(ymin = avg_ygaze - sd_ygaze, ymax = avg_ygaze + sd_ygaze), alpha = 0.4, fill = 'darkgreen') +
      facet_wrap(vars(participant), nrow = 1) +
      theme_bw() +
      labs(x = 'Time relative to onset stimulus (ms)',
           y = 'Vertical gaze deviation\n(pixels)') +
      theme(strip.text = element_blank())
```

```{r}
F2A / F2B / F2C
```

## Missing baselines

```{r}
# Number of trials with a missing baseline:
sum(is.na(dm$baseline))
# Number of trials with a Z-score <-2 or >2
sum(dm$bl_zscore < -2 | dm$bl_zscore > 2, na.rm = T)
# Total number of trials that were excluded based on baseline
sum(dm$bl_incl == 0)
# Number of succesfully baselined trials
sum(dm$bl_incl == 1)
```

## Figure 3: Gaze coordinates

```{r}
med_gaze <- dm %>%
  filter(trial == 1) %>%
  select(participant, medx_participant, medy_participant) 
```

```{r}
F3 <- dm_long %>%
  select(xtrace, ytrace, participant) %>%
  ggplot(aes(x = xtrace - 600, y = ytrace - 400)) +
  geom_hline(yintercept = 0, alpha = 0.6) +
  geom_vline(xintercept = 0, alpha = 0.6) +
  geom_hex() +
#  geom_point(data = med_gaze, aes(x = medx_participant - 600, y = medy_participant - 400), colour = 'red', size = 3) +
  facet_wrap(vars(participant)) +
  xlim(-600, 600) +
  ylim(-400, 400) +
  theme_bw() +
  labs(x = 'Gaze X-coordinate\nrelative to centre screen',
       y = 'Gaze Y-coordinate\nrelative to centre screen') +
  scale_fill_viridis_c()
```

```{r}
F3
```

## Table 3: Baseline-included trials

```{r}
table3 <- summary_combined %>%
  select(segment, participant, incl_bl) %>%
  pivot_wider(
    names_from = participant,
    values_from = incl_bl
  )

table3
```

## Figure 4: Baseline pupil sizes

```{r}
F4 <- dm %>%
  select(baseline, participant) %>%
  ggplot(aes(x = baseline)) +
  geom_histogram(fill = 'darkgreen', binwidth = 50, alpha = 0.5) +
  facet_wrap(vars(participant), scales = 'free_y') +
  theme_bw() +
  labs(x = "Baseline pupil size (A.U.)",
       y = 'Frequency')
```

```{r}
F4
```

## Figure 5: Excluded trials based on gaze deviation from participant median

```{r}
F5 <- dm %>%
  select(med_x, med_y, participant, gaze_incl, bl_incl) %>%
  ggplot(aes(x = med_x - 600, y = med_y - 400, colour = as.factor(gaze_incl))) +
  geom_hline(yintercept = 0, alpha = 0.6) +
  geom_vline(xintercept = 0, alpha = 0.6) +
  geom_circle(data = med_gaze, aes(x0 = medx_participant - 600, y0 = medy_participant - 400, r = 250), 
             fill = 'cyan', colour = adjustcolor('cyan', alpha.f = 0.1), alpha = 0.1, inherit.aes = F) +
  geom_point(alpha = 0.8) +
  facet_wrap(vars(participant)) +
  xlim(-600, 600) +
  ylim(-400, 400) +
  theme_bw() +
  labs(x = 'Gaze X-coordinate\nrelative to centre screen',
       y = 'Gaze Y-coordinate\nrelative to centre screen') +
  scale_fill_viridis_c() +
  theme(legend.position = 'none')
```

```{r}
F5
```

## Table 4: Gaze-included trials

```{r}
table4 <- summary_combined %>%
  select(segment, participant, incl_gaze) %>%
  pivot_wider(
    names_from = participant,
    values_from = incl_gaze
  )

table4
```

## Table 5: All included trials

```{r}
table5 <- summary_combined %>%
  select(segment, participant, incl) %>%
  pivot_wider(
    names_from = participant,
    values_from = incl
  )

table5
```

## Figure 6: Pupil traces

```{r}
dm_long %>%
  dplyr::filter(pupil_sample_incl == 1) %>%
  ggplot(aes(x = time, y = lppupil, group = index, colour = as.factor(trial))) +
  geom_line(alpha = 0.5) +
  facet_wrap(vars(participant), scales = 'free_y') +
  theme_bw() +
  labs(y = "Pupil size",
       x = 'Time (ms) from onset stimulus') +
  theme(legend.position = 'none')
```

## TRIAL EXCLUSION

```{r}
# Remove inf5 from the datasets
dm <- dm[dm$participant != "inf5", ]
dm_long <- dm_long[dm_long$participant != "inf5", ]

# Trial exclusion
list_inclusion <- list(baseline = which(dm$bl_incl == 1),
                       gaze = which(dm$gaze_incl == 1),
                       data_loss = which(dm$trial_incl == 1))

ggVennDiagram(list_inclusion)

with(dm,
     table(bl_incl, gaze_incl, trial_incl, exclude = NULL))

dm_long_clean <- dm_long[dm_long$include == 1, ]
dm_clean <- dm[dm$include == 1, ]
```

## Figure 7: all traces together, smoothed

```{r}
# Define onset (always 0)
stim_onset <- 0

# Define variable duration range
stim_dur_min <- min(dm$dur * 1000)
stim_dur_max <- max(dm$dur * 1000)
stim_dur_mid <- mean(c(stim_dur_min, stim_dur_max))

dm_long_clean %>%
  dplyr::filter(time < 3950, pupil_sample_incl == 1) %>%
  ggplot(aes(x = time, y = lppupil)) +

  # Shaded window (stimulus period range)
  annotate("rect",
           xmin = stim_dur_min, xmax = stim_dur_max,
           ymin = -Inf, ymax = Inf,
           fill = "lightgrey", alpha = 0.2) +
  
  # baseline
  geom_hline(yintercept = 0, colour = "black") +
  
  # Smooth trace
  geom_smooth(se = TRUE, linewidth = 1, colour = "darkgreen") +

  # Horizontal band above x-axis showing duration variability
  annotate("rect",
           xmin = stim_dur_min, xmax = stim_dur_max,
           ymin = 32, ymax = 33,   # adjust height to your data
           fill = "darkgrey", alpha = 0.6) +
    # Horizontal band above x-axis showing duration variability
  annotate("rect",
           xmin = stim_onset, xmax = stim_dur_min,
           ymin = 32, ymax = 33,   # adjust height to your data
           fill = "darkgrey") +

  # Dashed vertical lines for min/max duration
  annotate("segment", x = stim_dur_min, xend = stim_dur_min,
           y = 31.5, yend = 33, colour = "black", 
           linetype = "dashed") +
  annotate("segment", x = stim_dur_max, xend = stim_dur_max,
           y = 31.5, yend = 33, colour = "black", 
           linetype = "dashed") +

  # Stimulus onset arrow
  annotate("segment", x = stim_onset, xend = stim_onset,
           y = 33, yend = -Inf,
           colour = "black") +
  annotate("text",
           x = stim_onset, y = 33.5,
           label = "stimulus onset",
           vjust = 0, hjust = 0.4, size = 4.5, fontface = "italic") +

  # Label for duration range (above y-axis)
  annotate("text",
           x = stim_dur_mid, y = 33.5,
           label = "stimulus offset",
           hjust = 0.5, vjust = 0, size = 4.5, fontface = "italic") +

  # Formatting
  labs(y = "Pupil size (A.U.)", 
       x = "Time (ms) from stimulus onset") +
  coord_cartesian(ylim = c(-5, 35)) +
  theme_bw(base_size = 15) +
  theme(
    panel.grid = element_blank(),
    axis.title = element_text(face = "bold"),
    plot.margin = margin(15, 20, 15, 20)
  )
```

## Supplementary figure: fig. 7 per participant

```{R}
dm_long_clean %>%
  dplyr::filter(time < 3950 & pupil_sample_incl == 1) %>%
  ggplot(aes(x = time, y = lppupil)) +
  geom_rect(aes(xmin = min(dm$dur * 1000), xmax = max(dm$dur * 1000), ymin = -Inf, ymax = Inf), 
            inherit.aes = FALSE, fill = 'grey') +
  geom_hline(yintercept = 0) +
  geom_smooth(se = TRUE, linewidth = 1, colour = "darkgreen") +
  labs(y = "Pupil size",
       x = 'Time (ms) from onset stimulus') +
  theme_bw() +
  facet_wrap(vars(participant))
```

## Calculate metrics for statistical analysis: mean pupil response

```{r}
library(pracma)  
library(lmerTest)

# define analysis window: 200–2000 ms
win_start <- 200
win_end   <- 2500

PDR_summary <- dm_long_clean %>%
  group_by(index, participant, trial, type, segment, baseline) %>%
  summarise(
    auc = {
      sel <- time >= win_start & time <= win_end
      if (any(sel)) trapz(time[sel], pupil[sel]) else NA_real_
    },
    mean_response = mean(pupil[time >= win_start & time <= win_end], na.rm = TRUE),
    auc_lp = {
      sel <- time >= win_start & time <= win_end
      if (any(sel)) trapz(time[sel], lppupil[sel]) else NA_real_
    },
    mean_response_lp = mean(lppupil[time >= win_start & time <= win_end], na.rm = TRUE),
    .groups = "drop",
    mean_200_1200 = mean(pupil[time >= win_start & time <= 1200], na.rm = TRUE),
    mean_1200_2200 = mean(pupil[time >= 1200 & time <= 2200], na.rm = TRUE),
    mean_200_2000 = mean(pupil[time >= 200 & time <= 2000], na.rm = TRUE)
  )
```

## Research question 1: Does the pupil respond to auditory stimuli?

```{r}
## Assumption of normally distributed data
hist(PDR_summary$mean_response, 
     main = 'Histogram of mean pupil sizes (200-2500ms)',
     xlab = 'Mean pupil size',
     breaks = seq(-300, 200, by = 25))

qqnorm(PDR_summary$mean_response)
qqline(PDR_summary$mean_response)

t.test(PDR_summary$mean_response)
t.test(PDR_summary$mean_response[PDR_summary$index != 7])
```

## Figure 7b: Mean pupil size boxplot

```{r}
# Create a dummy spacer row
PDR_summary_combined <- PDR_summary %>%
  mutate(participant = as.character(participant)) %>%
  bind_rows(
    PDR_summary %>%
      mutate(participant = "All")
  ) %>%
  bind_rows(
    tibble(participant = " ", mean_response = NA, type = 'noise')  # spacer
  )

# Factor order: sorted participants, spacer, then All
PDR_summary_combined$participant <- factor(
  PDR_summary_combined$participant,
  levels = c(sort(unique(PDR_summary$participant)), " ", "All")
)

n_participants <- length(unique(PDR_summary$participant))

ggplot(PDR_summary_combined, aes(x = participant, y = mean_response)) +
  geom_hline(yintercept = 0, colour = "black", linetype = "dashed") +
  # Boxplots
  geom_boxplot(aes(fill = participant), colour = 'black',
               width = 0.6, outlier.shape = NA) +
  geom_jitter(width = 0.15, height = 0, alpha = 0.5) +
  # Axis labels
  labs(x = "Participant", y = "Mean pupil size (200–2500 ms)") +
  # Fill colors (participants, spacer, All)
  scale_fill_manual(
    values = c(
      RColorBrewer::brewer.pal(n = n_participants, "Set1"),  # participants
      "grey60"  # All
    )
  ) +
    # Bold "All" label with markdown
  scale_x_discrete(
    labels = c(unique(PDR_summary$participant), "",
               "<b>All participants</b>")  # bold markdown for 'All'
  ) +
  theme_bw(base_size = 15) +
  theme(
    panel.grid = element_blank(),
    axis.title = element_text(face = "bold"),
    legend.position = "none",
    axis.text.x = element_markdown(),
    axis.title.x = element_text(hjust = 0.3)  # adjust until centered visually
  )

```

## Figure 8: traces smooth for types

```{R}
dm_long_clean %>%
  dplyr::filter(time < 3950, pupil_sample_incl == 1) %>%
  ggplot(aes(x = time, y = lppupil, group = index, colour = type)) +

  # Shaded window (stimulus period range)
  annotate("rect",
           xmin = stim_dur_min, xmax = stim_dur_max,
           ymin = -Inf, ymax = Inf,
           fill = "lightgrey", alpha = 0.2) +
  
  # baseline
  geom_hline(yintercept = 0, colour = "black") +
  
  # Smooth trace
  geom_smooth(aes(group = type), se = TRUE, linewidth = 1) +

  # Horizontal band above x-axis showing duration variability
  annotate("rect",
           xmin = stim_dur_min, xmax = stim_dur_max,
           ymin = 34, ymax = 35,   # adjust height to your data
           fill = "darkgrey", alpha = 0.6) +
    # Horizontal band above x-axis showing duration variability
  annotate("rect",
           xmin = stim_onset, xmax = stim_dur_min,
           ymin = 34, ymax = 35,   # adjust height to your data
           fill = "darkgrey") +

  # Dashed vertical lines for min/max duration
  annotate("segment", x = stim_dur_min, xend = stim_dur_min,
           y = 32.5, yend = 35, colour = "black", 
           linetype = "dashed") +
  annotate("segment", x = stim_dur_max, xend = stim_dur_max,
           y = 32.5, yend = 35, colour = "black", 
           linetype = "dashed") +

  # Stimulus onset arrow
  annotate("segment", x = stim_onset, xend = stim_onset,
           y = 35, yend = -Inf,
           colour = "black") +
  annotate("text",
           x = stim_onset, y = 35.5,
           label = "stimulus onset",
           vjust = 0, hjust = 0.4, size = 4.5, fontface = "italic") +

  # Label for duration range (above y-axis)
  annotate("text",
           x = stim_dur_mid, y = 35.5,
           label = "stimulus offset",
           hjust = 0.5, vjust = 0, size = 4.5, fontface = "italic") +

  # Formatting
  labs(y = "Pupil size (A.U.)", x = "Time (ms) from stimulus onset") +
  theme_bw(base_size = 15) +
  theme(
    panel.grid = element_blank(),
    axis.title = element_text(face = "bold"),
    plot.margin = margin(15, 20, 15, 20),
    legend.position = c(0.97, 0.97),
    legend.justification = c("right", "top"),
    legend.background = element_rect(fill = "white", colour = "grey80"),
    legend.key = element_rect(fill = "white")
  )
```

## Supplementary figure: fig. 8 per participant

```{R}
dm_long_clean %>%
  dplyr::filter(time < 3950 & pupil_sample_incl == 1) %>%
  ggplot(aes(x = time, y = lppupil, group = index, colour = type)) +
  geom_rect(aes(xmin = min(dm$dur * 1000), xmax = max(dm$dur * 1000), ymin = -Inf, ymax = Inf), 
            inherit.aes = FALSE, fill = 'grey') +
  geom_hline(yintercept = 0) +
  geom_smooth(aes(group = type), se = TRUE, linewidth = 1) +
  labs(y = "Pupil size",
       x = 'Time (ms) from onset stimulus') +
  theme_bw()+
  theme(legend.position = 'bottom') +
  facet_wrap(vars(participant))
```

## Research question 2: Is there a difference between noise and language trials?

```{r}
model_simple <- lmer(mean_response ~ type + (1 | participant),
                     data = PDR_summary)
confint(model_simple)
summary(model_simple)
visualize(model_simple)
```

## Figure 8b: boxplots per type

```{r}
# Plot
ggplot(PDR_summary_combined, aes(x = participant, y = mean_response, fill = type)) +
  geom_hline(yintercept = 0, colour = "black", linetype = "dashed") +
  # Boxplots
  geom_boxplot(position = position_dodge(width = 0.7), width = 0.6, outlier.shape = NA) +
  # Points with jitter + dodge
  geom_point(
    position = position_jitterdodge(
      dodge.width = 0.7,  # same as boxplot dodge
      jitter.width = 0.1   # horizontal jitter within each type
    ),
    alpha = 0.6
  ) +
  # Labels
  labs(x = "Participant", y = "Mean response") +
  # Bold "All" label
  scale_x_discrete(labels = c(sort(unique(PDR_summary$participant)), "", "<b>All participants</b>")) +
  theme_bw(base_size = 15) +
  theme(
    panel.grid = element_blank(),
    axis.title = element_text(face = "bold"),
    legend.position = "top",
    axis.text.x = element_markdown(),
    axis.title.x = element_text(hjust = 0.3)
  )
```

## Figure 9: HPP data

```{r}
headturn_test <- read.csv("./data/raw/headturn/headturn-test-1.csv", skip = 1, sep = ";")
# Add the general participant labels
# ppid == 'pilot1' ~ 'inf1', and ppid == 'inf_pilot5' ~ 'inf5' are not included
headturn_test <- headturn_test %>%
  mutate(participant = case_when(ppid == 'pilot1' ~ 'inf1',
                                 ppid == 'inf_pilot2' ~ 'inf2',
                                 ppid == 'test_pilot1' ~ 'inf3',
                                 ppid == 'inf_pilot4' ~ 'inf4',
                                 ppid == 'inf_pilot5' ~ 'inf5')) %>%
  dplyr::filter(!is.na(participant)) %>%
  mutate(test_type = factor(test_type, levels = c("TT_FAMILIAR", "TT_UNGRAMMATICAL", "TT_NEW_GRAMMATICAL")))

# Precompute median per participant and test type
headturn_summary <- headturn_test %>%
  group_by(participant, test_type) %>%
  dplyr::filter(looking_time_ms > 1000) %>%
  summarise(median_time = median(looking_time_ms, na.rm = TRUE),
            mean_time = mean(looking_time_ms, na.rm = TRUE),
            .groups = "drop")
```


```{r}
ggplot(headturn_summary[headturn_summary$participant %in% c('inf2', 'inf3', 'inf4'),], 
       aes(x = test_type, y = mean_time, fill = test_type)) +
  geom_bar(stat = "identity") +
  geom_point(data = headturn_test[headturn_test$participant %in% c('inf2', 'inf3', 'inf4') & headturn_test$looking_time_ms > 1000,], 
             aes(y = looking_time_ms), alpha = 0.3) +
  labs(x = "", y = "Median looking time (ms)") +
  theme_bw(base_size = 15) +
  facet_wrap(vars(participant), ncol = 3) +
  theme(legend.position = 'none') +
  scale_x_discrete(labels = c(
    "TT_FAMILIAR"       = "Familiar",
    "TT_UNGRAMMATICAL"  = "Un-\ngrammatical",
    "TT_NEW_GRAMMATICAL"= "New\nGrammatical"
  ))
```

